Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-07-16 paper/current/main.tex
change continent to region

\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/big_embedding_picture.pdf}
	\caption{
		\textbf{Projection of embedding demonstrates complex multi-scale structure.}
		\textbf{a.}
		UMAP projection \autocite{mcinnes2018umap} of the embedding space reveals strong country-level clustering.
		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019. 
		Color indicates the continent.
		\textbf{b.} Zooming into (re-projecting) the area containing countries in the Middle East and South and Southeast Asia shows a geographic and cultural gradient of country clusters. 
		\textbf{c.} Similarly, zooming into the area organizations in Spain, Portugal, South, and Central America show clustering by majority language group--Spanish and Portuguese.
		\textbf{d.} Doing the same for organizations in the United States reveals geographic clustering based on state, roughly grouped by Census Bureau-designated regions,
		\textbf{e.} Zooming in further on Massachusetts reveals clustering based on urban center (Boston, Worcester), organizational sector (hospitals vs. universities), and university systems and prestige (UMass system vs. Harvard, MIT, etc.).
	}
	\label{fig:projection}
\end{figure}

@@

We quantify the relative importance of geography (by continent), and language (by majority language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, the similarity is based on higher levels.
Fig. \ref{fig:clustering}b demonstrates that the continent plays a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
This suggests that geography, then language, are important factors contributing to the structure of international scientific mobility.

>>>>

\begin{figure}[hp!]
	\centering
	\includegraphics[width=\textwidth]{\figdir/Projection/big_embedding_picture.pdf}
	\caption{
		\textbf{Projection of embedding demonstrates complex multi-scale structure.}
		\textbf{a.}
		UMAP projection \autocite{mcinnes2018umap} of the embedding space reveals strong country-level clustering.
		Each point corresponds to an organization and its size indicates the average annual number of mobile and non-mobile authors affiliated with that organization from 2008 to 2019. 
		Color indicates the region.
		\textbf{b.} Zooming into (re-projecting) the area containing countries in the Middle East and South and Southeast Asia shows a geographic and cultural gradient of country clusters. 
		\textbf{c.} Similarly, zooming into the area organizations in Spain, Portugal, South, and Central America show clustering by majority language group--Spanish and Portuguese.
		\textbf{d.} Doing the same for organizations in the United States reveals geographic clustering based on state, roughly grouped by Census Bureau-designated regions,
		\textbf{e.} Zooming in further on Massachusetts reveals clustering based on urban center (Boston, Worcester), organizational sector (hospitals vs. universities), and university systems and prestige (UMass system vs. Harvard, MIT, etc.).
	}
	\label{fig:projection}
\end{figure}

@@

We quantify the relative importance of geography (by region), and language (by majority language of each country) using the element-centric clustering similarity~\autocite{gates2019element}, a method that can compare hierarchical clustering by explicitly adjusting the relative importance of different levels of the hierarchy with scaling parameter $r$, acting like a ``zooming lens''.
If $r$ is high, the similarity is based on the lower levels of the dendrogram, whereas when $r$ is low, the similarity is based on higher levels.
Fig. \ref{fig:clustering}b demonstrates that the region plays a major role at higher levels of the clustering process (low $r$), and language (family) explains the clustering more at the lower levels (high $r$).
This suggests that geography, then language, are important factors contributing to the structure of international scientific mobility.
